Determinants of Soccer Players' Market Values in Major European League(s)

### 2024-12-04 paper/paper.qmd
Final Update

---
title: "Determinants of Soccer Players' Market Values in Major European League(s)"
subtitle: "Goals, Assists, and Age Dominate, While League-Specific Patterns Add Complexity"
author: 
  - John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
abstract: "The global soccer transfer market is shaped by diverse factors influencing player valuations across leagues. This study analyzes determinants of market value in five major European leagues using data from the 2023/24 season. Goals and assists consistently emerge as the strongest predictors, with the Premier League valuing goals highest and the Bundesliga emphasizing assists, while age negatively affects value across all leagues, particularly in La Liga. These observations highlight universal trends and league-specific valuation dynamics, offering actionable guidance for clubs, agents, and analysts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Summarize numeric variables
numeric_summary <- england_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    Minutes = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for France
numeric_summary_france <- france_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    Minutes = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Germany
numeric_summary_germany <- germany_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    Minutes = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Italy
numeric_summary_italy <- italy_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    Minutes = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Spain
numeric_summary_spain <- spain_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    Minutes = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

## Alternative Models and Future Directions

@@

ggplot(assists_data, aes(x = League, y = Estimate, fill = League)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = round(Estimate, 3)), vjust = -0.25, size = 3) +
  scale_fill_manual(values = c(
    "England" = "#D62728",
    "France" = "#1F77B4",
    "Germany" = "#000000",
    "Italy" = "#2CA02C",
    "Spain" = "#FFB000"
  )) +
  theme_minimal() +
  labs(
    x = "League",
    y = "Assists Coefficient (in Million Euros)"
  )
```

@@

![Example to Get National Team Ranking Data](../other/photos/National_Team_Ranking.png){#fig-national_team_ranking fig-pos="H"}

@@

![Example to Get Club Ranking Data](../other/photos/Club_Ranking.png){#fig-club_ranking fig-pos="H"}

>>>>

---
title: "Determinants of Soccer Players' Market Values in Major European League(s)"
subtitle: "Goals, Assists, and Age Dominate while League-Specific Patterns Add Complexity"
author: 
  - John Zhang
thanks: "Code and data are available at: https://github.com/Clearsky21z/Player_Market_Value_Analysis"
date: today
date-format: long
abstract: "The global soccer transfer market is shaped by diverse factors influencing player valuations across leagues. This study analyzes determinants of market value in five major European leagues using data from the 2023/24 season. Goals and assists consistently emerge as the strongest predictors, with the Premier League valuing goals highest and the Bundesliga emphasizing assists, while age negatively affects value across all leagues, particularly in La Liga. These observations highlight universal trends and league-specific valuation dynamics, offering actionable guidance for clubs, agents, and analysts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Summarize numeric variables
numeric_summary <- england_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    `Minutes Played` = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for France
numeric_summary_france <- france_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    `Minutes Played` = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Germany
numeric_summary_germany <- germany_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    `Minutes Played` = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Italy
numeric_summary_italy <- italy_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    `Minutes Played` = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

# Summarize numeric variables for Spain
numeric_summary_spain <- spain_data %>%
  select(
    market_value_million,
    age,
    goals,
    assists,
    club_ranking,
    national_team_ranking,
    minutes_played
  ) %>%
  rename(
    `Market Value (in Million Euros)` = market_value_million,
    Age = age,
    Goals = goals,
    Assists = assists,
    `Club Ranking` = club_ranking,
    `National Team Ranking` = national_team_ranking,
    `Minutes Played` = minutes_played
  ) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Value") %>%
  group_by(Variable) %>%
  summarize_numeric()

@@

## Alternative Models

@@

ggplot(assists_data, aes(x = League, y = Estimate, fill = League)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::label_number(accuracy = 0.001)(Estimate)), 
            vjust = -0.25, size = 3) +
  scale_fill_manual(values = c(
    "England" = "#D62728",
    "France" = "#1F77B4",
    "Germany" = "#000000",
    "Italy" = "#2CA02C",
    "Spain" = "#FFB000"
  )) +
  theme_minimal() +
  labs(
    x = "League",
    y = "Assists Coefficient (in Million Euros)"
  )
```

@@

![Example to Retrieve National Team Ranking Data](../other/photos/National_Team_Ranking.png){#fig-national_team_ranking fig-pos="H"}

@@

![Example to Retrieve Club Ranking Data](../other/photos/Club_Ranking.png){#fig-club_ranking fig-pos="H"}
